---
title       : Study the relationship between variables and MPG
subtitle    : dataset of mtcars
author      : AndyLiu0429
job         : Pitch Presentation
framework   : io2012        
highlighter : highlight.js  
hitheme     : tomorrow       
widgets     : [bootstrap]            # {mathjax, quiz, bootstrap}
mode        : selfcontained # {standalone, draft}
knit        : slidify::knit2slides
---

## mtcars dataset - Description

### Motor Trend Car Road Tests

> The data was extracted from the 1974 Motor Trend US magazine, and comprises fuel consumption and 10 aspects of automobile design and performance for 32 automobiles (1973–74 models).

### Source
> Henderson and Velleman (1981), Building multiple regression models interactively. Biometrics, 37, 391–411.

```{r}
library(datasets)
head(mtcars, 3)
```

---

## mtcars dataset - Format

**The data contains with 32 observations on 11 variables.**

| Index | Field | Detail |
------- | ----- | ------ |
| [, 1] | mpg | Miles/(US) gallon |
| [, 2]  | cyl | Number of cylinders |
| [, 3]    | disp | Displacement (cu.in.) |
| [, 4]    | hp | Gross horsepower |
| [, 5]    | drat | Rear axle ratio |
| [, 6]	| wt | Weight (lb/1000) |
| [, 7]	| qsec | 1/4 mile time |
| [, 8]	| vs | V/S |
| [, 9]	| am | Transmission (0 = automatic, 1 = manual) |
| [,10]	| gear | Number of forward gears |
| [,11]	| carb | Number of carburetors |

---

## Analysis - Fitting linear regression model

### The following example shows the relationship between cylindar and mpg
### Choose the variables by clicking on different variables' names on my shinyApp
- URL: *http://swhgoon.github.io/devdataprod-cp/part2_devdataprod-slidify*

```{r}
model <- lm(mpg~cyl,data=mtcars)
plot(mtcars$cyl,mtcars$mpg,xlab="Number of cylindars",ylab="mpg",main="relationship between cyl and mpg")
abline(model, col=2)
```

---

## Analysis - Conducting Regression Analysis

### The t-test tests whether should we accept the regression coefficients
### The F-test tests whether should we accept the regression equation

```{r}
summary(model)
```
